\textit{Supplementary materials for:} Fitness tracking reveals task-specific associations between memory, mental health, and exercise

### 2021-10-20 paper/supplement.tex
working on supplement figure captions (backing up progress)

\begin{figure}[p]
\centering
\includegraphics[width=0.6\textwidth]{figs/vocab_learning_behavior}
\caption{\textbf{Foreign language vocabulary learning behavioral
    results.}  \textbf{a. Immediate recall....}}
\label{fig:vocab_behavioral}
\end{figure}

>>>>

\begin{figure}[p]
\centering
\includegraphics[width=0.6\textwidth]{figs/vocab_learning_behavior}
\caption{\textbf{Foreign language vocabulary learning behavioral
    results.}  \textbf{a. Immediate recall.}  Average proportions of
  correctly identified Gaelic-English word pairs from \textit{early} (first 3) and
\textit{late} (last 3) study positions, or aggregated over
\textit{all} study positions.  \textbf{b. Distribution of proportion
  of correctly recalled pairs on the immediate memory test.}  The colored
lines indicate quartile boundaries, and correspond to the coloring in
Panel a.  Note that the right-most edge of the third quartile overlaps
with the top quartile, since over 25\% of the participants correctly recalled
90\% of the word pairs correctly, but no participant achieved 100\%
accuracy.  \textbf{c--d. Delayed recall.}  These panels are in the
same formats as Panels a and b, but reflect performance on the delayed
recall test.  The error bars in Panels a and c denote
bootstrap-estimated 95\% confidence intervals.}
\label{fig:vocab_behavioral}
\end{figure}
